Open Split Tests

### 2021-06-13 inst/rmd/opensplittests.Rmd
Add latest run.

```{r}
carb_data <- tribble(~, ~name, ~rec_num, ~mass,
                     1, "C-2_1", 1082, 6.03,
                     2, "C-2_2", 1082, 11.10,
                     3, "C-2_3", 1082, 15.52
                     )

@@

insert_raw(df)
```

@@

@@

insert_results(df_sum)
```

@@

@@

```{r}
cons <- df_sum %>% 
  filter(as.numeric(Pos) > 4,
         !is.na(fm_consensus)) %>% 
  select(Sample.Name, fm_consensus, fm_corr, sig_fm_corr) %>% 
  mutate(Fm_diff = fm_corr - fm_consensus,
         sigma = amstools::sigma(fm_corr, fm_consensus, sig_fm_corr)) %>% 
  arrange(Sample.Name)

knitr::kable(cons)
```

>>>>

```{r}
carb_data <- tribble(~number, ~name, ~rec_num, ~mass,
                     1, "C-2_1", 1082, 6.03,
                     2, "C-2_2", 1082, 11.10,
                     3, "C-2_3", 1082, 15.52
                     )

@@

#insert_raw(df)
```

@@

```{r}
df %>% 
  filter(pos > 2) %>% 
  plot_hgis_time(norm_ratio, sig_norm_ratio, outlier = !.$ok_calc) +
  ggtitle("Sample ratio vs. time")
```

```{r}
df %>% 
  filter(pos > 2) %>% 
  plot_hgis_time(he12C, outlier = !.$ok_calc) +
  ggtitle("Sample current vs time")
```

@@

#insert_results(df_sum)
```

```{r}
df_sum %>% 
  filter(pos > 2) %>% 
  mutate(he12C = he12C*1E6) %>% 
  select(Positon = pos, `Sample Name` = sample_name, `12C Current (uA)` = he12C, n_runs, fm_corr, sig_fm_corr) %>% 
  arrange(`Sample Name`)
```

@@

```{r}
df_sum %>% 
  filter(pos > 2) %>% 
  compare_replicates()
```

@@

```{r}
cons <- df_sum %>% 
  filter(pos > 2,
         !is.na(fm_consensus)) %>% 
  select(sample_name, fm_consensus, fm_corr, sig_fm_corr) %>% 
  mutate(fm_diff = fm_corr - fm_consensus,
         sigma = amstools::sigma(fm_corr, fm_consensus, sig_fm_corr)) %>% 
  arrange(sample_name)
cons  
knitr::kable(cons)
```
